Algebraic properties of CFT coset construction and Schramm-Loewner evolution

### 2011-10-10 AffineLieAlgebras/SLE/article.tex
Bibliography on SLE is added.

  SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT. Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions.

  Minimal models can be obtained from WZNW models by coset construction. Then it is natural to study SLE with additional Brownian motion on coset space $G/H$. We discuss algebraic properties of coset fields and correlation functions which correspond to SLE observables. 
\end{abstract}

\section{Introduction}
\subsection{Schramm-Loewner evolution}
To remind of Schramm-Loewner evolution we first describe simple example.

>>>>

  We generalize Schramm-Loewner evolution with additional Brownian motion on Lie group to the case of direct product of two groups. We then study connection between SLE description of critical behavior with coset models of conformal field theory. In order to be consistent such construction should give minimal models for certain choice of groups.

%%    SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT. Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions. 
%%  
%%    Minimal models can be obtained from WZNW models by coset construction. Then it is natural to study SLE with additional Brownian motion on coset space $G/H$. We discuss algebraic properties of coset fields and correlation functions which correspond to SLE observables. 
\end{abstract}

\section{Introduction}
Schramm-Loewner evolution, introduced by Oded Schramm in papers \cite{schramm2000scaling} is

\subsection{Schramm-Loewner evolution}
To remind of Schramm-Loewner evolution we first describe simple example.
